---
title: "SQL"
output: html_document
---

## Filtering Rows and Columns 

With SQL, you can filter columns with SELECT and rows with WHERE. Let's look at an example using the Lahman baseball database. First, we need to load some packages. 

``` {r warning=FALSE, message=FALSE}
library(Lahman)
library(sqldf)
```


#Suppose we want to see the homerun totals for the 1927 Yankees. We could write the following:
 

```{r}
query<-"SELECT playerID,yearID,teamID,HR FROM Batting
WHERE teamID='NYA' and yearID=1927"
sqldf(query)
```

#Suppose we want to find out the amount of Yankees players that have hit 40 or more homeruns. We could write the following:

```{r}
query<-"SELECT playerID,yearID,teamID,HR FROM Batting
WHERE teamID='NYA' and HR>=40"
sqldf(query)
```

#Adding the Strike Outs into the query we can further filter out which players hit over 40 homeruns AND had less than 60 strike outs with the following:

```{r}
query<-"SELECT playerID,yearID,teamID,HR,SO FROM Batting
WHERE HR>=40 and SO<60"

sqldf(query)
```

#Finally we’re filtering all the teams to just the Phillies, query the years in the 1970’s (using a range), and finally extract the players with more than 30 homeruns:

```{r}
query<-"SELECT playerID,yearID,teamID,HR FROM Batting
WHERE teamID='PHI' and HR>30 and yearID<=1979 and yearID>=1970"

sqldf(query)
```

#Now were going to find all the players that hit more than 50 homeruns going from the greatest number to the lowest:

```{r}
query<-"SELECT playerID,yearID,teamID,HR FROM Batting
WHERE HR>50
ORDER BY HR DESC"

sqldf(query)
```

#Finally, we’re going to find the players with less than 10 srtikeouts with atleast 400 at-bats:

```{r}
query<-"SELECT playerID,yearID,teamID,SO,AB FROM Batting
WHERE SO<10 and AB>=400 
ORDER BY SO"

sqldf(query)
```

#I'm just practicing. Let's add some more code.

```{r}
query<-"SELECT HR FROM Batting
WHERE playerID= 'ruthba01'"

sqldf(query)
```

```{r}
query<-"SELECT playerID, sum (HR) FROM Batting
WHERE playerID='ruthba01'
GROUP BY playerID"

sqlf(query)
```

```{r}
query<-"SELECT playerId, sum(HR) FROM Batting
GROUP BY playerID
HAVING sum(HR)>600
ORDER BY sum(HR) DESC"

sqldf(query)
```

```{r}
query<-"SELECT nameFirst,nameLast,yearID,teamID,HR 
FROM Batting INNER JOIN Master
ON Batting.playerID=Master.playerID
WHERE Batting.playerID='ruthba01'"
sqldf(query)
```

```{r}
query<-"SELECT nameFirst,nameLast,yearID,teamID,HR
FROM Batting INNER JOIN Master
ON Batting.playerID=Master.playerID
WHERE HR>50
ORDER BY HR DESC"

sqldf(query)
```

```{r}
query<-"SELECT playerID,name,Batting.yearID,Batting.HR
FROM Batting INNER JOIN Teams
ON Batting.teamID=Teams.teamID AND Batting.yearID=Teams.yearID
WHERE playerID='ruthba01'"

sqldf(query)
```

