---
title: "SQL"
output: html_document
---

## Filtering Rows and Columns 

With SQL, you can filter columns with SELECT and rows with WHERE. Let's look at an example using the Lahman baseball database. First, we need to load some packages. 

``` {r warning=FALSE, message=FALSE}
library(Lahman)
library(sqldf)
```


Suppose we want to see the homerun totals for the 1927 Yankees. We could write the following:
 

```{r}
query<-"SELECT playerID,yearID,teamID,HR FROM Batting
WHERE teamID='NYA' and yearID=1927"
sqldf(query)
```

Suppose we want to find out the amount of Yankees players that have hit 40 or more homeruns. We could write the following:

```{r}
query<-"SELECT playerID,yearID,teamID,HR FROM Batting
WHERE teamID='NYA' and HR>=40"
sqldf(query)
```

```{r}
query<-"SELECT playerID,yearID,teamID,HR,SO FROM Batting
WHERE HR>=40 and SO<60"

sqldf(query)
```

```{r}
query<-"SELECT playerID,yearID,teamID,HR FROM Batting
WHERE teamID='PHI' and HR>30 and yearID<=1979 and yearID>=1970"

sqldf(query)
```

```{r}
query<-"SELECT playerID,yearID,teamID,HR FROM Batting
WHERE HR>50
ORDER BY HR DESC"

sqldf(query)
```

```{r}
query<-"SELECT playerID,yearID,teamID,SO,AB FROM Batting
WHERE SO<10 and AB>=400 
ORDER BY SO"

sqldf(query)
```

